---
title: "Lab 1"
date: January 15, 2022
author: Amy, Ksenia, and Rebecca
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE)

library(rio)
library(tidyverse)
library(here)
library(ggridges)
library(tidytext)
```

```{r read-in-data, echo = FALSE}
twitstats <- readRDS(here("data", "rstats_tweets.rds")) %>% 
	as.data.frame()
#twitstats
```

### 1. Initial exploration  
#### Create histograms and density plots of `display_text_width`. Try at least four different binning methods and select what you think best represents the data for each. Provide a brief justification for your decision.
```{r initial-exploration}
#ggplot(twitstats, aes(x = display_text_width)) +
#	geom_histogram(fill = "#56B4E9",
#								 color = "white",
#								 alpha = 0.9,
#								 bins = 50)

#ggplot(twitstats, aes(x = display_text_width)) +
#	geom_histogram(fill = "#56B4E9",
#								 color = "white",
#								 alpha = 0.9,
#								 bins = 35)

#ggplot(twitstats, aes(x = display_text_width)) +
#	geom_histogram(fill = "#56B4E9",
#								 color = "white",
#								 alpha = 0.9,
#								 bins = 25)

ggplot(twitstats, aes(x = display_text_width)) +
	geom_histogram(fill = "#56B4E9",
								 color = "white",
								 alpha = 0.9,
								 bins = 5)

ggplot(twitstats, aes(x = display_text_width)) +
	geom_density(aes(fill = is_quote),
							 color = "white",
							 alpha = 0.4)

ggplot(twitstats, aes(x = display_text_width, y = is_quote)) +
	ggridges::geom_density_ridges(color = "white",
																fill = "#A9E5C5")

```

##### Binning of 5 is the best for the histogram because it shows the distribution of the data with the fewest bars which makes it easier to understand.

### 2. Look for "plot"  

#### Search the `text` column for the word “plot.” 
(Note I played around with different functions and also counting tweets containing "plot" vs. all instances of "plot.")
```{r search-plot, eval = FALSE}
# stringr logical - returns T/F for each row. Evaluates whether the word "plot" is in the tweet. 
str_detect(twitstats$text, "plot")

# stringr logical - returns T/F for each row (tweet). Evaluates whether the word "plot" as a whole word is in the tweet. 
str_detect(twitstats$text, "\\bplot\\b")

# Base R logical - returns T/F for each row (tweet). Evaluates whether the word "plot" is in the tweet.
grepl("plot", twitstats$text)

# Base R - returns vector of row #s where tweet contains "plot." 
grep("plot", twitstats$text)

# Base R - returns vector of row #s where tweet contains "plot" as a whole word.  
grep("\\bplot\\b", twitstats$text)

# For each row (tweet), returns the number of instances of "plot." 
str_count(twitstats$text, "plot")

# For each row (tweet), returns the number of instances of "plot" as a whole word.
str_count(twitstats$text, "\\bplot\\b")
```

```{r calculate-plot}
# Returns the number of tweets containing "plot."
sum(str_detect(twitstats$text, "plot"))

# Returns the number of tweets containing "plot" as a whole word. 
sum(str_detect(twitstats$text, "\\bplot\\b"))

# Returns the total number of instances of variations of "plot" across all tweets. 
sum(str_count(twitstats$text, "plot"))

# Returns the total number of instances of "plot" as a whole word across all tweets.
sum(str_count(twitstats$text, "\\bplot\\b"))
```

#### Report the proportion of posts containing this word.
```{r proportion-plot}
# Calculate the number of rows (i.e., tweets) in the dataset.
twitstats %>% 
  nrow()

# Calculate the percentage of tweets that contain "plot."
round(((sum(str_detect(twitstats$text, "plot"))) / nrow(twitstats)) * 100, 2)

# Calculate the percentage of tweets that contain "plot" as a whole word.
round(((sum(str_detect(twitstats$text, "\\bplot\\b"))) / nrow(twitstats)) * 100, 2)
```

##### Of the `r format(nrow(twitstats), big.mark=",",scientific=FALSE)` tweets in the 2019 #tidytuesday Week 1 dataset, `r round(((sum(str_detect(twitstats$text, "plot"))) / nrow(twitstats)) * 100, 2)`% of tweets contained the word "plot" in some variation (e.g., plot, plots, plotting, ggplot) and `r round(((sum(str_detect(twitstats$text, "\\bplot\\b"))) / nrow(twitstats)) * 100, 2)`% contained "plot" as a distinct whole word.  

### 3. Plot rough draft
```{r plot-draft}
#Structuring the tweets data by turning it into a simple data frame
twitstats_df <- tibble(
  paragraph = seq_along(twitstats$text),
  description = twitstats$text
)
#Breaking it into individual words
twitstats_words <- twitstats_df %>% 
  unnest_tokens(word, description)

#Removing "t.co", "https", "http", "rt", "rstats"
twitstats_contentwords <- subset (twitstats_words, !(twitstats_words$word %in% c("t.co", "https", "http", "rt", "rstats")))

#Plotting the 15 most common words represented in the posts excluding stop words
twitstats_contentwords %>% 
  anti_join(stop_words) %>%
  count(word, sort = TRUE) %>% 
  mutate(word = fct_reorder(word, n)) %>% 
  slice(1:15) %>% 
  ggplot(aes(n, word)) +
  geom_col()
    
```

### 4. Stylized Plot
```{r plot-stylized}
#creating the stylized plot
stylized.plot <- twitstats_contentwords %>% 
  anti_join(stop_words) %>%
  count(word, sort = TRUE) %>% 
  mutate(word = fct_reorder(word, n)) %>% 
  slice(1:15) %>% 
  ggplot(aes(n, word)) +
  geom_col(fill = "cornflowerblue",
           color = "white",
           alpha = 0.8) +
  labs(title    = "Word frequencies in posts",
       subtitle = "Top 15 words displayed",
       x        = "Count",
       y        = "Word")
#changing the text sides
text_settings <- 
  theme(plot.title = element_text(size = 20)) +
  theme(plot.subtitle = element_text(size = 16)) +
  theme(axis.title.x = element_text(size = 16)) +
  theme(axis.title.y = element_text(size = 16)) +
  theme(axis.text.x = element_text(size = 12)) +
  theme(axis.text.y = element_text(size = 12)) 

#removing all horizontal and minor vertical grids; changing the position of title & subtitle; printing the plot
stylized.plot + 
  theme_minimal()+
  theme(panel.grid.major.x = element_line(size = 0.5, linetype = 'solid',
                                colour = "gray"), 
  panel.grid.major.y = element_blank(), 
  panel.grid.minor.x = element_blank(), 
  panel.grid.minor.y = element_blank(),
  plot.title = element_text(hjust = -0.15),
  plot.subtitle = element_text(hjust = -0.12))+ 
  text_settings

```

